% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Zhipeng XIONG}

\basicInfo{
  \email{zhipeng@akane.waseda.jp} \textperiodcentered\ 
  \phone{(+81) 080-8490-1247} \textperiodcentered\ 
  \linkedin[Zhipeng XIONG]{https://www.linkedin.com/in/zhipeng-xiong-2023012a3}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Waseda University}, Kitakyushu, Japan}{2023 -- Present}
\textit{Master student} in Data Engineering (Natural Languague Processing), expected July 2025
\datedsubsection{\textbf{University of Electronic Science and Technology of China}, Chengdu, China}{2020 -- 2024}
\textit{B.S.} in Computer Science and Technology (CS) GPA: 3.6/4.0
\datedsubsection{\textbf{University of California, Berkeley}}{2021}
\textit{Summer Exchange}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Text-Generation Large Language Model Project}}{2023 -- 2024}
\role{Python, Pytorch, Transformers, Linux}{Undergraduate Graduation Project}
Brief introduction: Analyze bloggers' social relationships and generate the text with a fusion of styles.
\begin{itemize}
  \item Implemented automatically collecting and processing data feature, based on a GitHub Open Source Project.
  \item Fine-tuned an Open Source Large Language Model, allowing it to better generate text in the style of the target.
\end{itemize}

\datedsubsection{\textbf{College Assistant - Student Affairs}}{2022 -- 2023}
\role{Teaching Assistant}{Part-time Job}
Brief introduction: Assist the teachers in handling student affairs.
\begin{itemize}
  \item Assisted in hosting educational lectures and activities.
  \item Administered general office support, including answering questions, filing and record keeping.
\end{itemize}


\datedsubsection{\textbf{Artboard and Game 2048 Projects}}{Sep. 2021 -- 2022}
\role{Python, Tkinter, Linux}{Individual Projects}
Brief introduction: An artboard and the 2048 video game, based on the Python Tkinter GUI.
\begin{itemize}
  \item Easily customizable and extendable.

\end{itemize}


\datedsubsection{\textbf{Information Management System}}{Sep. 2021 -- 2022}
\role{C++, QT, SQL}{Individual Project}
A compact and efficient information management system, built using the C++ QT GUI and a MySQL database.
\begin{itemize}
  \item Linked the local MySQL database with the C++ QT GUI, and easy to be expanded to cloud database.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python > Git == Docker > SQL > C++ == C
  \item Platform: Linux
  \item Development: Natural Language Processing, Data Engineering
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{University-level Prize}, Award on Social Practice }{July. 2021}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: \url{https://github.com/XIONG-ZHIPeng}
  \item Languages: English - CEFR-B2 (TOEIC: 835), Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
